Proposte applicative per ZKP

### 2022-04-28 Resources/proposte_applicative_zkp.tex
Update 13: Modified resources + Added some testing with CIRCOM

	- > \url{https://www.moesif.com/blog/blockchain/ethereum/Tutorial-for-building-Ethereum-Dapp-with-Integrated-Error-Monitoring/}

>>>>

	- > \url{https://www.moesif.com/blog/blockchain/ethereum/Tutorial-for-building-Ethereum-Dapp-with-Integrated-Error-Monitoring/} \\ \\
	- > zkDApp with Circom, Solidity, Truffle, snarkJS: \\
		Blog Post: \url{https://kndrck.co/posts/practical_guide_build_zk_dapps/} \\
		Repo: \url{https://github.com/kendricktan/hello-world-zk-dapp} \\\
